%!TEX root = ../main.tex

\chapter{Summary}

In this survey, we discussed the challenges of hardware accelerator design and the barriers for designers to catch up with the growth of design complexity.
We used the Y-chart model to define different level of abstractions for designing hardware accelerators and showed to increase design productivity we need to automate the transition process between behavioral to structural domain.
We provided examples of processor and system-level synthesis and showed because of missing semantics between different domains going from behavioral description to structural description is challenging.

In the related work section, we first looked at the traditional HDL languages and discussed different language extensions that tried to increase the productivity of hardware design.
We argued while there are advances in design productivity with the introduction of HCLs and hardware compiler frameworks like FIRRTL but why such approaches still are aboard to increase the productivity of the whole system design.
Then we looked at different HLS tools and describe how these tools synthesis a system from languages such as C/C++.
We discussed the different type of synthesis techniques, different scheduling methods and elaborated more on the disadvantage of each approach.

\paragraph{Conclusion:}
Unfortunately, current HLS approaches suffer from two broad limitations that make them ill suited for exploring different microarchitecture,
i) they are based on the control-driven Von-Neumann execution  model,  whereas  accelerator  architecture typically adopt a dataflow-based execution model,
and ii) they only represent execution behavior and the actual structural components of a microarchitecture is fixed.
Therefore, they limit the capability of compiler to explore different designs and limit their technique to suite only a specific type of workload.
Current HLS tools, are aware of these limitations and encourage users to scatter structural hints in the behavior description in C. However, this closely ties in behavioral correctness with microarchitecture structures, requires are challenging to modify.
We believe an alternative is to decouple the representation used for accelerator microarchitecture and hardware optimizations from the functional behavior specification. This technique can address both of these limitations.